SAT Competition 2020\tnoteref{title}

### 2020-12-17 paper/main.tex
some incremental track talk

\todo{MS; look at what Marcus already wrote}

@@

Ihe incremental library track was first introduced in SAT~Race~2015 and then took place again in SAT~Competitions 2016 and 2017. 
Numerous applications, e.g., SMT solvers or SAT-based planners, use SAT solvers incrementaly, i.e., formulas are repeatedly refined between solve-calls. 
One important contribution of the founders of this track is the specification of the general incremental interface IPASIR (Re-entrant Incremental Solver API) for SAT applications~\cite{Balyo:2015:SATRace}. 
In SAT~Competitions 2020, we run the track again and selected a total $300$ benchmark instances for the six applications described below.

>>>>

In the Incremental Library track we mimic scenarios
where a SAT solver is used as a backend solver in a more complex tool
(typically solving a harder problem than SAT) and is called multiple times before 
the enclosing tool reaches its final state. Incrementality means that
the individual calls to the SAT solver are not independent, but may share 
a common subset of the input clauses or differ in the presence of additional 
unit clause assumptions \cite{TODO}.

Instead of using or extending the DIMACS input format, we realize the Incremental track
by relying on the general incremental interface IPASIR (Re-entrant Incremental Solver API) 
for SAT applications~\cite{Balyo:2015:SATRace}. The idea is that we actually run the 
enclosing tool on its own benchmark and communicate with the competing SAT solver 
through this interface API. Not only does the SAT solver in this track
need to solve a sequence of related problems fast, but its answers to the early questions
may in general influence which questions will follow next.

@@

The incremental library track was first introduced in SAT~Race~2015 and 
then took place again in SAT~Competitions 2016 and 2017. 
Numerous applications, e.g., SMT solvers or SAT-based planners,
use SAT solvers incrementally, i.e., formulas are repeatedly refined between the solver calls.
In SAT~Competitions 2020, we selected a total \num{300} benchmark instances for the Incremental track
from the six applications described below.
